Figures and Tables

### 2021-01-15 paper/figures_tables.Rmd
Figures 1 and 2

>>>>

```{r libraries}
library(ggplot2)
library(aracari)
library(cowplot)
library(dplyr)

```{r}
# Simulate the data for one run

set.seed(5)

data(ptpl)

# Panel 2: Table with gut retention times and the gamma distribution used for it
n <- 10000
grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
tt <- max(grt_data$time)
ggplot(grt_dens, aes(x = dat)) +
  geom_density() + 
  geom_point(data = grt_data, aes(x = time, y = 0), color = "red") +
  #geom_point(aes(x = tt, y = 0), color = "red") +
  theme_bw() + labs(x = "Time in minutes", y = "Density") -> fig_GRT

# Panel 3: Exponential distribution used for animal movement lengths
rate <- 1/mean(ptpl$mpm)
md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
md_hist <- data.frame(md = round(sample(md_dens$dat, tt)))

ggplot(md_dens, aes(x = dat)) +
  geom_density() + 
  geom_point(data = md_hist, aes(x = md, y = 0)) +
  theme_bw() + labs(x = "Distance in meters", y = "Density") -> fig_MD

ggplot(md_hist, aes(x = md)) +
  geom_histogram() +
  theme_bw() + labs(x = "Distance in meters", y = "Count") -> fig_MD_hist

# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
set.seed(5)
distance <- md_hist$md
angle <- runif(tt, min = 0, max = 360)
distx <- distance*cos(angle)
xloc <- c(0, cumsum(distx))
disty <- distance*sin(angle)
yloc <- c(0, cumsum(disty))
animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
seed_loc <- merge(animalTraj, grt_data, by = "time")
mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))

ggplot() +
  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_traj

ggplot() +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_disp

ggplot() +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  #geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue", size = 4) +
  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y), linetype = "dashed", color = "blue") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_agg

## Figure 1. 
Density distributions from which we sample gut retention time (GRT) and movement distance (MD).

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
#ggsave("testfig.tiff", dpi = 300, width = 3, units = "in")
```

## Figure 2.
Simulation example where animal movement determines location for seeds dropped. Calculations for seed dispersal distance from the parent tree and seed distance to the mean seed location as a measure of aggregation.

```{r fig.height=2, fig.width=6}
plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
```

## Figure 3.
Variation in Weibull distributions determined by the value of the shape parameter. The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.

```{r}
# shape
exptail <- 1
thintail <- 0.2
fattail <- 2

#scale
b <- 1
kappaexp <- b^-exptail
kappathin <- b^-thintail
kappafat <- b^-fattail

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
                color = "black", linetype = "dashed", size = 1.2) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
                color = "black", linetype = "dotted", size = 1.2) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
                color = "black", linetype = "solid", size = 1.2) +
  ylab("") + xlab("") +
  theme_bw()

## Figure 4. 
Seed dispersal kernels produced by the three models considered

```{r}
